---
title: "Dictionary"
author: "Annie"
date: "February 23, 2019"
output: html_document
---

#Dictionary

##General bits
1. help(topic)
This searches the R help desk and retrieves information about what you are searching for.
```{r}
help("summary.aov") #provides a description of this function and general directions on how to use it
```


2. ?topic
This function provides information about how particular pieces of syntax work. 
```{r}
?topic <- data.frame
```


3. ls()
Not exactly sure what this function is doing but it appears to have created 2 lists based on previously existing values in the environment.
```{r}
ls(1,2)

```


4. dir()
This lists the names of each file in the R project.
```{r}
dir()
```


5. list.files()
This function lists all the names of each file in a given R project.
```{r}
list.files()
```


##Input and output
1. save()
This saves an R object to a file.
```{r}
x <- 1
save("x", file = "testfile.txt")
```


2. load()
This loads saved data.
```{r}
load(file = "testfile.txt")
```


3. data()
This function allows you to search for pre-made data sets in r
ex.
```{r}
?data
data()
```

4. library()
This code allows you to access a package and insert it into your code. Then it allows your package to work for the code chunk.
ex.
```{r}
library(ggplot2)
Names <- rep(c("Dara", "Azalea", "Barbi", "Rowena", "Fiona"),each=2)
MF <- rnorm(10, 45, 25)
Condition <- rep(c("Social", "Nonsocial"), 5)
Aversity <- rep(c("A", "N_A"), times=c(4,6))
plot_df <- data.frame (Names, MF, Condition, Aversity)

ggplot(plot_df, aes(x=Condition, y=MF, group=Names, 
                    linetype=Aversity))

```

5. read.table()
This reads a particular table and creates a data frame.
```{r}
read.table(file = "testfile.txt")
```


6. read.csv()
This function also read a particular table and creates a data frame.


7. scan()

8. print()
This function analyzes the results of your code (executing all the commands)
ex.
```{r}
data.frame(1,2,3,4)
print(data.frame())
```

9. cat()

10. write.table()

##Data Creation
1. c()
This function is used to combine elements (factors in a vectore for example)
```{r}
c(1,2,3,4,5)
```


2. from:to (where from and to are replaced with numbers, e.g. 1:10)
This lists all the numbers in a specified range.
```{r}
1:10
```


3. seq()
Not exactly sure what is happening here but it appears that this function is using the first two numbers to help derive the third.
```{r}
seq(2,10,7)
```


4. rep()
This function replicates the first number the number of times that is designated in the second space
```{r}
rep(1,10)
```


5. data.frame()
This allows one to enter specific groups of data values
ex.
```{r}
data.frame(1, 2, 3, 5)
```

6. list()
This provides a numbered list for all objects in a set.
```{r}
list(2,6,1,3,8)
```


7. matrix()

8. factor()

9. rbind()
This function allows you to bind a new row to an existing data frame
```{r}
df <- rbind(df,
          random_number=runif(dim(df)[1],0,1))
```

10. cbind()
This funtion allows you to bind a new column to an existing data frame
```{r}
df <- cbind(df,
          random_number=runif(dim(df)[1],0,1))
```


##Slicing and extracting data indexing vectors
x[n] nth element
x[-n] all but nth element
x[1:n] first n elements
x[-(1:n)] elements from n+1 to the end
x[c(1,4,2)] specific elements
x[“name”] elements named “name”
x[x>3] all elements greater than 3
x[x > 3 & x < 5] all elements between 3 and 5
x[x %in% c(“a”,“and”,“the”)] all elements in given set

##Indexing lists
x[n] list with elements n
x[[n]] nt h element of the list
x[[“name”]] element of the list named “name”
x$name id.

##Indexing matrices
x[i,j] element at row i, column j
x[i,] row i
x[,j] column j
x[,c(1,3)] columns 1 and 3
x[“name”,] row named “name”
Indexing data frames (matrix indexing plus the following)
x[[“name”]] column named “name”
x$nameid.

##Variable conversion
as.data.frame(x)
as.numeric(x)
as.logical(x)
as.character(x)

##Variable information
1.is.na(x)
2.is.null(x)
3.is.data.frame(x)
4.is.numeric(x)
5.is.character(x)
6.length(x)
7.dim(x)
This funtion provides the number of rows and columns in a data frame without the data
```{r}
library(dplyr)

df <- starwars

dim(df)
```
8.dimnames(x)
This function lists the names of the categories in a data frame
```{r}
library(dplyr)

df <- starwars

dimnames(df)
```
9.nrow(x)
10.ncol(x)
11.class()
12.attributes()

##Data selection and manipulation
1.which.max()
2.which.min()
3.which()
4.sort()
5.unique()
6.table()
7.sample()

##Math
1.max()
This sets the maximum value included in a data set.
```{r}
x <- c(1,2,3,4,5,10)
max(x)
```


2.min()
This set the minimum value included in a data set.
```{r}
x <- c(1,10,20,100)
min(x)
```


3.range()
This determines the range of numbers considered in a set.
```{r}
x <- c(1, 10, 20, 40, 100)
range(x)
```


4.sum()
This function adds all the numbers in a given set.
```{r}
x <- c(1, 10, 20, 40, 100)
sum(x)

```


5.mean()
Creates the mean of a given set of number values.
```{r}
x <- c(1, 10, 20, 40, 100)
mean(x)
```


6.median()
calculates the median of a set of numbers.
```{r}
x <- c(1, 10, 20, 40,  100)
median(x)
```


7.var()
This calculates the variance of a set of values.
```{r}
x <- c(1, 10, 20, 40, 100)
var(x)
```

8.sd()
This calculates the standard deviation of a set of values.
```{r}
x <- c(1, 10, 20, 40, 100)
sd(x)
```

9.cor()
This calculates the correlation between groups of data.
```{r}
x <- c(1, 10, 20, 40, 100)
y <- c(50, 60, 100, 200, 300)
cor(x,y)
```

10.round()
This rounds a decimal to a specified number of decimals.
```{r}
round(5.4567,1)
```

11.abs()
This takes the absolute value of a given number.
```{r}
abs(-20)
```


##Matrices
t()
diag()
rowSums()
colSums()
rowMeans()
colMeans()

##Advanced Data processing
apply()
aggregate()
Strings
paste()
strsplit()
tolower()
toupper

##Plotting
hist()
This function creates a histogram graph of a given set of data.
```{r}
x <- c(1,20,50)
hist(x)
```


plot()
This function creates a plot graph of a given set of data.
```{r}
x <- cbind(c(1,2,3,4),c(10,20,30,40))
plot(x)
```


##Distributions
rnorm()
This function inserts a normal distribution.
```{r}
rnorm(100, mean = 50, sd=2)
```


runif()

##Programming
show that you can define a function
show that you can write a for loop
show that you can write a while loop
show that you can write an if else statement
Explain what return() does inside a function, show you can use it
Explain what break() does, show you can use it

##Installing some packages
Use the packages tab in R-studio to install these packages. You will need to be connected to the internet when you do this. If you are installing on your laptop, or on R-studio Cloud, then these packages will not need to installed again.

1.ggplot2
```{r}
library(ggplot2)
```

2.dplyr
```{r}
library(dplyr)
```

3.shiny

4.data.table
```{r}
library(data.table)
```

5.reshape2


6.stringr
