---
title: "Dictionary"
author: "Joschka Schwarz"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 3
    code_folding: show
---

<style>
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #2DC6D6;
}
</style>

# Helpful code chunks
## General bits

1. `?function_name`
This function provides information about how particular pieces of syntax work. 

```{r}
?list.files
```

2. `list.files()`
This function lists all the names of each file in a given R project.
```{r}
list.files()
```

...

***

## Input and output
1. `saveRDS()`
This saves an R object to a file.
```{r}
x <- 1
saveRDS("x", file = "testfile.rds")
```


2. `readRDS()`
This loads saved data.
```{r}
x <- readRDS(file = "testfile.rds")
```

...

***

## Data Creation
1. `c()`
This function is used to combine elements (factors in a vectore for example)
```{r}
numbers <- c(1,2,3,4,5)
numbers <- c(1:5)
print(numbers)
```


2. `seq()`
Generates a sequence of numbers. The first two values are the starting and (maximal) end values of the sequence. The third is the step width of the sequence.
```{r}
seq(1,10,2)
```

3. `rep()`
This function replicates the first number the number of times that is designated in the second space
```{r}
rep(1,10)
```


4. `data.frame()
This allows one to enter specific groups of data values
```{r}
df <- data.frame(col_A = c(1, 2, 3, 5), col_B = c("A", "B", "C", "D"))
df
```

6. list()
This provides a numbered list for all objects in a set.
```{r}
list(c(2,6,1,3,8))
```

9. `rbind()` and  `cbind()`
This function allows you to bind a new row to an existing data frame
```{r}
col_C  <- c(TRUE, FALSE, FALSE, TRUE)
df_new <- rbind(df, col_C)
```


## Slicing and extracting data indexing vectors
* `x[n]` nth element
* `x[-n]` all but nth element
* `x[1:n]` first n elements
* `x[-(1:n)]` elements from n+1 to the end
* `x[c(1,4,2)]` specific elements
* `x[“name”]` elements named “name”
* `x[x>3]` all elements greater than 3
* `x[x > 3 & x < 5]` all elements between 3 and 5
* `x[x %in% c(“a”,“and”,“the”)]` all elements in given set

## Indexing lists
x[n] list with elements n
x[[n]] nt h element of the list
x[[“name”]] element of the list named “name”
x$name id.

## Indexing matrices
x[i,j] element at row i, column j
x[i,] row i
x[,j] column j
x[,c(1,3)] columns 1 and 3
x[“name”,] row named “name”
Indexing data frames (matrix indexing plus the following)
x[[“name”]] column named “name”
x$nameid.

## Variable conversion
as.data.frame(x)
as.numeric(x)
as.logical(x)
as.character(x)

## Variable information
1.is.na(x)
2.is.null(x)
3.is.data.frame(x)
4.is.numeric(x)
5.is.character(x)
6.length(x)
7.dim(x)
9.nrow(x)
10.ncol(x)
11.class()
12.attributes()

## Data selection and manipulation
1.which.max()
2.which.min()
3.which()
4.sort()
5.unique()
6.table()
7.sample()

## Math
1.max()
This sets the maximum value included in a data set.
```{r}
x <- c(1,2,3,4,5,10)
max(x)
```


2.min()
This set the minimum value included in a data set.
```{r}
x <- c(1,10,20,100)
min(x)
```


3.range()
This determines the range of numbers considered in a set.
```{r}
x <- c(1, 10, 20, 40, 100)
range(x)
```


4.sum()
This function adds all the numbers in a given set.
```{r}
x <- c(1, 10, 20, 40, 100)
sum(x)

```


5.mean()
Creates the mean of a given set of number values.
```{r}
x <- c(1, 10, 20, 40, 100)
mean(x)
```


6.median()
calculates the median of a set of numbers.
```{r}
x <- c(1, 10, 20, 40,  100)
median(x)
```


7.var()
This calculates the variance of a set of values.
```{r}
x <- c(1, 10, 20, 40, 100)
var(x)
```

8.sd()
This calculates the standard deviation of a set of values.
```{r}
x <- c(1, 10, 20, 40, 100)
sd(x)
```

9.cor()
This calculates the correlation between groups of data.
```{r}
x <- c(1, 10, 20, 40, 100)
y <- c(50, 60, 100, 200, 300)
cor(x,y)
```

10.round()
This rounds a decimal to a specified number of decimals.
```{r}
round(5.4567,1)
```

11.abs()
This takes the absolute value of a given number.
```{r}
abs(-20)
```


## Matrices
t()
diag()
rowSums()
colSums()
rowMeans()
colMeans()

## Advanced Data processing
apply()
aggregate()
Strings
paste()
strsplit()
tolower()
toupper

## Plotting
hist()
This function creates a histogram graph of a given set of data.
```{r}
x <- c(1,20,50)
hist(x)
```


plot()
This function creates a plot graph of a given set of data.
```{r}
x <- cbind(c(1,2,3,4),c(10,20,30,40))
plot(x)
```


## Distributions
rnorm()
This function inserts a normal distribution.
```{r}
rnorm(100, mean = 50, sd=2)
```


## Programming
show that you can define a function
show that you can write a for loop
show that you can write a while loop
show that you can write an if else statement
Explain what return() does inside a function, show you can use it
Explain what break() does, show you can use it

## Installing some packages
Use the packages tab in R-studio to install these packages. You will need to be connected to the internet when you do this. If you are installing on your laptop, or on R-studio Cloud, then these packages will not need to installed again.
